\large{\bf Looking forwards and backwards through locally regulated populations }

### 2023-04-16 forwards-and-backwards.tex
minor edits

{\bf Reproduction parameters:}
We assume that 
\begin{enumerate}
\item The function $F(x,m)$ satisfies 
    \begin{enumerate}
    \item $F(x,m)$ is locally Lipschitz in $m$;
    \item $F(x,m)$ is uniformly bounded above (but not necessarily below);
    \item for each fixed $m$, $\sup_{x\in\IR^d}\sup_{k\leq m}|F(x,k)|<\infty$;
    \end{enumerate}
\item The functions $r(x,m)$, $\gamma(x,m)$ have bounded first and second 
    derivatives in both arguments;
    \label{r_gamma_derivs_condition}
\item $\gamma(x,m)$ is uniformly bounded;
    \label{gamma_bounded_condition}
\item For each $f \in C_b^2(\IR^d)$, there is a $C_f$ such that
    $$ |\gamma(x, \smooth{\gamma} \eta(x)) \theta \int 
    (r(y, \smooth{r} \eta(y)) f(y) - r(x, \smooth{r} \eta(x)) f(x))
    q_\theta(x, dy)| \le C_f $$
    for all $x \in \IR^d$ and $\eta \in \measures$.
        \label{gamma_B_condition}
\end{enumerate}

To keep expressions manageable, we shall also assume that 
\[
\mu_\theta(x) = r(x, \smooth{r} X(x) / N) \gamma(x, \smooth{\gamma} X(x) / N)
        - \frac{1}{\theta} F(x, \smooth{F} X(x) / N),
\]
that is, this expression is non-negative so that there is no need to take the maximum
	with zero in~(\ref{eqn:mu_defn}). (This is anyway true for 
	sufficiently large $\theta$.)
\end{assumptions}

\comment{TODO: modify condition (4) to say that the $C_f$ only depends on $\|f\|_\infty$, $\|\partial f\|$ and $\|\partial^2 f\|$: PETER}

@@

If $r(x,m)$ is independent of $m$, then the conditions are easy to 
satisfy; they just require some regularity of $r$ as a function of $x$. 
Condition~\ref{control through r} is also satisfied if for example
$\|\nabla\rho_r\|\leq C\rho_r$ 
and $m\partial_mr(x,m)$, $m^2\partial_{mm}r(x,m)$ are bounded.
This is the case, for instance, if $\rho_r$ decays exponentially.
On the other hand, it might seem more natural to take $\rho_r$ to be a Gaussian 
density with parameter $\sigma_r$, say. Then, 
as we check in Lemma~\ref{lem:gamma_bound},
Condition~\ref{control through gamma} is satisfied if $\rho_\gamma$ is also
Gaussian with parameter $\sigma_\gamma$ and $\sigma_\gamma>\sigma_r$. For large enough
$\theta$, this condition guarantees that 
$\sigma_r+1/\theta <\sigma_\gamma$, so that the establishment probability of a juvenile
is controlled by individuals that are already `felt' by the fecundity kernel $\rho_\gamma$
at the location of their parent.

@@

 Writing
    $K_3 = \sup_{x,m} \max_i |\partial_{x_i} f(x)r(x, m)|$
    and 
    $K_4 = \sup_{x,m} \max_{i,j} |\partial_{x_i x_j} f(x)r(x, m)|$, since
\[\big|\partial_{x_i}\big(f(x)r(x,\rho_r*\eta(y))\big|\leq K_3\]
and
\[\big|\partial_{x_ix_j}\big(f(x)r(x,\rho_r*\eta(y))\big|\leq K_4,\]
the first term
is bounded exactly as above. For the second, 
    \begin{multline*}
        r(x, \smooth{r}\eta(y)) - r(x, \smooth{r}\eta(x))
        \\
=
        (\smooth{r}\eta(y) - \smooth{r}\eta(x)) r'(x,\smooth{r}\eta(x))
        + \frac{1}{2} (\smooth{r}\eta(y) - \smooth{r}\eta(x))^2 r''(x, \overline{m}),
    \end{multline*}
    where $\overline{m}= \kappa'\smooth{r}\eta(x) +(1-\kappa') 
\smooth{r}\eta(y)$ for some $0\leq \kappa'\leq 1$, and
    we have used $r'$ and $r''$ to denote the first and second derivatives of $r(x,m)$
with respect to the second argument.
    So, writing $K_5=\|f\|_\infty\|r'\|_\infty$ and $K_6=\|f\|_\infty\|r''\|_\infty$,
    the second term in~\eqref{eqn:q_bound_split} is bounded by
    \begin{align*}
       K_5
        \left|
            \theta \int_{\IR^d}
                (\smooth{r}\eta(y) - \smooth{r}\eta(x))
            q_\theta(x, dy)
        \right|
        +
       K_6
        \left|
            \theta \int_{\IR^d}
                (\smooth{r}\eta(y) - \smooth{r}\eta(x))^2
            q_\theta(x, dy)
        \right| .
    \end{align*}
Under Condition~\ref{control through gamma} of 
Assumptions~\ref{def:model_setup}, the right hand side is bounded by 
a constant times $\smooth{\gamma}\eta(x)+(\smooth{\gamma}\eta(x))^2$ and 
$m^2\gamma(m)$ is bounded, so therefore $|\gamma B^\theta_f|$ is bounded.
\end{proof}

@@

\begin{proof}[Sketch]
    \comment{Change this to a sequence $f_n$ of smooth things with uniformly bounded derivs that increase 1; follows from condition 4. PETER}
To avoid the idea being buried in notation, we sketch the proof in the 
special case of $d=1$ and $\DG=\Delta$.
For any $f\in C_b^\infty(\IR)$,
\begin{multline}
\label{special case first moment equation}
\IE[\langle f,\eta_t\rangle] 
=\IE[\langle f,\eta_0\rangle]
\\
+\IE\Big[\int_0^t\Big\langle\gamma(x, \smooth{\gamma}\eta_s(x))
\Delta \big(f(\cdot)r(\cdot,\smooth{r}\eta_s(\cdot))\big)(x)
+F(x,\smooth{F}\eta_s(x)) f(x),
\eta_s(dx)\Big\rangle ds\Big].
\end{multline} 
We take a sequence of test functions $f_n$ increasing to
$\exp(\lambda x)$, with $\lambda>0$. Having passed
to the limit,
substituted in~(\ref{special case first moment equation}) and 
expanded the term involving the Laplacian, we obtain
\begin{multline}
\label{exponential moment}
    \IE[\langle \exp(\lambda x),\eta_t\rangle]
    =
    \IE[\langle \exp(\lambda x),\eta_0\rangle]
    +
    \IE\Big[\int_0^t\Big\langle\gamma(x, \smooth{\gamma}\eta_s(x))
    \exp(\lambda x)
    \Big\{
        \lambda^2 r(x, \smooth{r}\eta_s(x))
    \\ {}
        + 2\lambda\partial_x\big(r(\cdot,\smooth{r}\eta_s(\cdot)\big)(x)
        + \partial_{xx} r(\cdot,\smooth{r}\eta_s(\cdot)\big)(x)
    \Big\} 
    + F(x,\smooth{F}\eta_s(x)),
    \eta_s(dx)\Big\rangle ds\Big] .
\end{multline} 
Evidently, in much the same way as in the proof of
Lemma~\ref{lem:eta_f_bound},
our conditions on $r$ and $F$ ensure
that the integrand on the right hand side 
of~(\ref{exponential moment})
is bounded by $C\langle\exp(\lambda x),\eta_s(dx)\rangle$ for some constant
$C$. Gronwall's inequality then implies that 
$\IE[\langle\exp(\lambda x),\eta_t(dx)\rangle]$ 
is uniformly bounded for $t\in [0,T]$, and an application of Markov's inequality
tells us that for any $\delta >0$,
$\IP[\eta_t([R,\infty])>\delta]\to 0$ as $R\to\infty$. A symmetric argument
yields the corresponding bound for $\IP[\eta_t([-\infty, -R])>\delta$ and the 
result is proved.
\end{proof}

@@

    We require that $\{(F(\lp^N_t))_{t \ge 0}\}_N$
    is tight as a sequence of real-valued c\`adl\`ag processes, for all $F$ in a subset
    of $\bar C(\lpmeasures)$, the bounded, continuous functions on $\lpmeasures$,
    that is dense with respect to uniform convergence on compact subsets.
    Lemma~\ref{lem:test_fn_tightness} shows that $\{\langle f, \lp^N_t \rangle\}_N$ is a tight sequence
    for any $f: \overline{\IR^d} \times [0,\infty) \to \IR$ with compact support
    in the level direction.
    The functions $\lp \mapsto \langle f, \lp \rangle$
    do not form not a dense subset of $\bar C(\lpmeasures)$,
    but they do separate points and vanish nowhere, so
    by the Stone-Weierstrass theorem, the algebra they generate is dense
    % in $C_0(\lpmeasures)$, the continuous functions that vanish at infinity
    % (i.e., are less than $\epsilon$ outside of a compact set, for any $\epsilon$).
    % Since $C_0(\lpmeasures)$ is dense
    in $\bar C(\lpmeasures)$ (with respect to uniform convergence on compact subsets).
    So, it suffices to show that tightness for the processes $\langle f, \lp^N_t\rangle$
    extends to finite sums and products of these processes,
    which is shown in Lemma~\ref{lem:product_tightness}.

    The analogue of Lemma~\ref{lem:limit_mgale},
    in particular that the martingale properties are preserved under passage to the limit,
    are proved in Section~\ref{sec:lookdown_generator_proofs}.
    \comment{TODO: refer to correct thing or just say "like in 6.6": PETER}
    Finally, we must show that the limiting lookdown process $\lp$
    projects to the limiting process $\eta$, i.e., a solution of the martingale
    problem in Theorem~\ref{thm:nonlocal_convergence}.
    Let $N_k \to \infty$ be a sequence along which $\lp^{N_k}$ converges.
    By Theorem~\ref{thm:nonlocal_convergence},
    there is a subsequence $N_{k(j)}$ along which the projected population processes
    $\eta^{N_{k(j)}}$ converge, and the limit solves the martingale problem.
    Thus any limit point of $\lp^N$ projects to a population process $\eta$
    solving the martingale problem of Theorem~\ref{thm:nonlocal_convergence}.
\end{proof}

@@

In this section we verify one of the conditions of the Markov Mapping Theorem,
namely, that ``integrating out levels'' in the generator of the lookdown process
we obtain the generator of the projected process.
We will work with test functions of the form
$$  f(\lp) = \prod_{(x, u) \in \lp} g(x, u) = \exp\left(\langle \log g, \lp \rangle \right) . $$
Furthermore, recall that $\kappa^N(\lp)(\cdot) = \lp(\cdot \times [0, N)) / N$
is the ``spatial projection operator'',
and define the probability kernel $\Gamma^N : \measures \to \mathcal{M}(\IR^d \times [0,N))$
so that for $\eta \in \measures$, if $\hat g(x) = \int_0^N g(x, u) du / N$, then
\begin{align*}
    F^N_g(\eta)
    &:=
    \int f(\lp) \Gamma^N(\eta, d\lp) \\
    &=
    \exp\left(
        N \left\langle
            \log \frac{1}{N} \int_0^N g(x, u) du, \eta(dx)
        \right\rangle
    \right) \\
    &=
    \exp\left(
        N \left\langle \log \hat g(x), \eta(dx) \right\rangle
    \right) ,
\end{align*}
i.e., $\Gamma^N$ assigns independent labels on $[0, N]$ to each of the points in $\eta$.
It follows from Lemma~\ref{def: MP definition of limit} that for test functions of this form
\comment{(TODO beware the different definition of $f$ to that lemma) PETER ``in order to adhere to standard notation in the literature''}
the generator of $\eta^N_t$ is
\begin{align} \label{eqn:pgen_defn_again}
    \begin{split}
    \Pgen^N F^N_g(\eta)
    =
    F^N_g(\eta)
        N \theta & \bigg\langle
        \gamma(x, \eta) \int r(z, \eta) \left( \hat g(z) - 1 \right) q_\theta(x, dz)
    \\ &\qquad \qquad {}
        +
        \mu_\theta(x, \eta) \left( \frac{1}{\hat g(x)} - 1 \right)
        ,
        \eta(dx)
    \bigg\rangle
    \end{split}
\end{align}
The generator of $\lp^N_t$ is $A^N$, defined in equation~\eqref{eqn:lookdown_generator}.

@@

For the limiting process,
we now require test functions such that $g(x,u) = 1$ for all $u$ larger than some $u_0$;
As before, recall that $\kappa(\lp)(\cdot) = \lim_{u \to \infty} \lp(\cdot \times [0, u)) / u$
is the ``spatial projection operator'',
and define the probability kernel $\Gamma : \measures \to \flpmeasures$
so that for $\eta \in \measures$,
defining $h(x) = \int_0^\infty (g(x, u) - 1) du$,
\begin{align*}
    F_g(\eta)
    &:=
    \int f(\lp) \Gamma(\eta, d\lp) \\
    &=
    \exp\left(
        \big \langle
            \int_0^\infty (g(x, u) - 1) du,
            \eta(dx)
        \big \rangle
    \right) \\
    &=
    e^{ \langle h(x), \eta(dx) \rangle } .
\end{align*}
i.e., $\Gamma(\eta, \cdot)$ is the distribution of a conditionally Poisson process
with intensity a product of $\eta$ and Lebesgue measure.
It again follows from Lemma~\ref{def: MP definition of limit} that for test functions of this form
\comment{(TODO beware the different definition of $f$ to that lemma) PETER}
the generator of $\eta_t$ is
\begin{align} \label{eqn:pgen_infty}
    \Pgen^\infty F_g(\eta)
    &=
    F_g(\eta)
    \left\langle
        \gamma(x, \eta)
        \DG( h(\cdot) r(\cdot) )(x)
        + F(x, \eta) h(x)
        + \alpha \gamma(x, \eta) r(x, \eta) h^2(x)
        ,
        \eta(dx)
    \right\rangle .
\end{align}
The generator of $\lp_t$ is $A$, defined in equation~\eqref{eqn:limiting_lookdown_generator}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Technical Lemmas}

\subsection{Gaussian Kernel Estimates}

\begin{lemma}\label{eq: Gaussin density estimates}
\begin{equation}
 \theta H_{\theta}(x,w)\rho_r(x-w)\leq \rho_{\gamma}(x-w),
\end{equation}
where
$$H_{\theta}(x,w)=\int_{\IR^d}
    \left(
        \frac{\rho_r(y-w)}{\rho_r(x-w)}
        -
        1
    \right)^2
q_{\theta}(x,dy).$$
\end{lemma}
\begin{proof}

Writing out $H$,
\begin{align}
H_\theta(x, w)
=
\int
    \left(
        \exp\left(
            - \frac{1}{2\epsilon_r^2}
            \left\{
                ||y - w||^2 - ||x - w||^2
            \right\}
        \right)
        -
        1
    \right)^2
    \frac{
        e^{-\theta (y - x-\meanq)^{T}\covq^{-1}(y - x-\meanq)  / 2}
    }{
        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
    }
dy.
\end{align}
Writing $z=y-x-\meanq$, we have that 
\begin{equation}
\begin{aligned}
||y - w||^2 - ||x - w||^2 
=& ||y||^2-||x||^2 -2\langle y-x, w\rangle \\
=&||x+z+ \meanq||^2-||x||^2-2 \langle z+ \meanq, w\rangle\\
=&2\langle x, z+ \meanq \rangle + ||z+ \meanq||^2-2 \langle z+ \meanq, w\rangle \\
=& 2 \langle x-w, z+ \meanq \rangle + ||z+ \meanq||^2\\
=& 2\langle x-w+ \meanq,\meanq \rangle + 2\langle x-w+ \meanq, z \rangle +||z||^2
\end{aligned}
\end{equation}
As a result, we have 
\begin{align}
H_\theta(x, w)
=&
\int
    \left(
        \exp\left(
            - \frac{1}{2\epsilon_r^2}
            \left\{
                2 \langle x-w, z+ \meanq \rangle + ||z+ \meanq||^2
            \right\}
        \right)
        -
        1
    \right)^2
    \frac{
        e^{-\theta z^{T}\covq^{-1}z  / 2}
    }{
        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
    }
dz\\
=&\exp\left(-\frac{2}{\epsilon_r^2}\langle x-w+ \meanq,\meanq \rangle \right)\\
& \times \int
        \frac{
        \exp\left(
            - \frac{2}{\epsilon_r^2} \langle x-w+ \meanq, z \rangle
            - \frac{1}{\epsilon_r^2} ||z||^2
            \right)
            e^{-\theta z^{T}\covq^{-1}z  / 2}
    }{
        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
    }
dz\\ \label{eq: Second moment term matrix calculation}
&-2\exp\left(-\frac{1}{\epsilon_r^2}\langle x-w+ \meanq,\meanq \rangle \right)\\
& \qquad \qquad \times     \int
    \frac{ \exp\left(
             -\frac{1}{\epsilon_r^2}\langle x-w+ \meanq, z \rangle
              -\frac{1}{2\epsilon_r^2} ||z||^2
            \right)e^{-\theta z^{T}\covq^{-1}z  / 2}
        }{
        (2 \pi/ \theta)^{d/2} |\covq|^{1/2} \label{eq: first moment term matrix calculation}
    }
dz\\
&+1.
\end{align}
We now consider the integral of the form 
\begin{equation}
\int \exp(v^{T}z-C||z||^2) \frac{
        e^{-\theta z^{T}\covq^{-1}z  / 2}
    }{
        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
    }
dz   
\end{equation}
for $v \in \IR^d$ and $C>0$. 
We have 
\begin{equation}
\begin{aligned}
&\int \exp(v^{T}z-C||z||^2) \frac{
        e^{-\theta z^{T}\covq^{-1}z  / 2}
    }{
        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
    }
dz\\
=&\frac{1}{|\covq|^{1/2}|  |\covq^{-1}(I+2C\covq/\theta )|^{1/2}  }\int \exp(v^{T}z) \frac{
        e^{-\theta z^{T}\covq^{-1}(I+2C\covq/\theta )z  / 2}
    }{
        (2 \pi/ \theta)^{d/2}|\covq^{-1}(I+2C\covq/\theta )|^{-1/2} 
    }
dz\\
=& \frac{1}{|I+2C\covq/\theta |^{1/2}} \mathbb{E}_{Z}[\exp (v^{T}Z)]\\
=&\frac{1}{|I+2C\covq/\theta |^{1/2}}
\exp 
\left(
\frac{1}{2}v^{T}\covq/\theta(I+2C\covq/\theta )^{-1}v
\right),
\end{aligned}
\end{equation}
where $Z \sim N(0, \covq/\theta \times (I+2C\covq/\theta )^{-1})$.

Now writing $v=\frac{2}{\epsilon_r^2}( w-x-\meanq)$
and $C=\frac{1}{\epsilon_r^2}$,
we have the expression in Equation
\eqref{eq: Second moment term matrix calculation} is 
$$\frac{1}{|I+2\covq/(\epsilon_r^2\theta) |^{1/2}}
\exp 
\left(
\frac{2}{\epsilon_r^4}( w-x-\meanq)^{T}\covq/\theta\left(I+2\covq/(\epsilon_r^2\theta)\right)^{-1}( w-x-\meanq)
\right).$$
Similarly, writing $v=\frac{1}{\epsilon_r^2}( w-x-\meanq)$
and $C=\frac{1}{2\epsilon_r^2}$,
we have the expression in Equation
\eqref{eq: first moment term matrix calculation} is 
$$\frac{1}{|I+\covq/(\epsilon_r^2\theta) |^{1/2}}
\exp 
\left(
\frac{1}{2\epsilon_r^4}( w-x-\meanq)^{T}\covq\left(I+\covq/\theta/(\epsilon_r^2\theta)\right)^{-1}( w-x-\meanq)
\right).$$
As a result, we have 
\begin{align*}
&H_{\theta}(x,w)\\
=& \frac{1}{|I+2\covq/(\epsilon_r^2\theta) |^{1/2}}
\exp 
\left(
\frac{2}{\epsilon_r^4}( w-x-\meanq)^{T}\covq/\theta\left(I+2\covq/(\epsilon_r^2\theta)\right)^{-1}( w-x-\meanq)
\right)\\
&-2\frac{1}{|I+\covq/(\epsilon_r^2\theta) |^{1/2}}
\exp 
\left(
\frac{1}{2\epsilon_r^4}( w-x-\meanq)^{T}\covq/\theta\left(I+\covq/(\epsilon_r^2\theta)\right)^{-1}( w-x-\meanq)
\right)\\
&+1.
\end{align*}
If we write $F(1/\theta)=H_{\theta}(x,w)$, i.e.
\begin{align*}
&F(s)\\
=& \frac{1}{|I+2/\epsilon_r^2 \covq s |^{1/2}}
\exp 
\left(
\frac{2}{\epsilon_r^4}( w-x-\meanq)^{T}\covq s \left(I+2/\epsilon_r^2 \covq s\right)^{-1}( w-x-\meanq)
\right)\\
&-2\frac{1}{|I+2/\epsilon_r^2 \covq s |^{1/2}}
\exp 
\left(
\frac{1}{2\epsilon_r^4}( w-x-\meanq)^{T}\covq s \left(I+2/\epsilon_r^2 \covq s\right)^{-1}( w-x-\meanq)
\right)\\
&+1\\
&=G_1(s)+2G_2(s)+1
\end{align*}
we can check that $F(0)=0$.
As a result, 
$$\theta H_{\theta}(x,w)\rho_r(x-w)= \theta F(1/\theta)\rho_r(x-w)=F'(s)\rho_r(x-w),$$
for some $s \in [0, 1/\theta]$.

In Equation \eqref{eq: gamma-r convolution comparison}, we have established that 
$\rho_r(x-w) / \rho_\gamma(x-w) = C' \exp(-K (x-w)^2 / 2)$
with $K = \frac{1}{\epsilon_r^2} - \frac{1}{\epsilon_\gamma^2}$.
Therefore it suffices to show that for all $x,w \in \IR^d$ and $s \in [0, 1/\theta]$, 
\begin{align}\label{eqn:goal3}
    F'(s) \exp\left(-A (x-w)^2 \right) \le C .
\end{align}

>>>>

{\bf Reproduction parameters:}
We assume that 
\begin{enumerate}
\item The function $F(x,m)$ satisfies 
    \begin{enumerate}
    \item $F(x,m)$ is locally Lipschitz in $m$;
    \item $F(x,m)$ is uniformly bounded above (but not necessarily below);
    \item for each fixed $m$, $\sup_{x\in\IR^d}\sup_{k\leq m}|F(x,k)|<\infty$;
    \end{enumerate}
\item The functions $r(x,m)$, $\gamma(x,m)$ have bounded first and second 
    derivatives in both arguments;
    \label{r_gamma_derivs_condition}
\item $\gamma(x,m)$ is uniformly bounded;
    \label{gamma_bounded_condition}
\item For each $f \in C_b^2(\IR^d)$,
    there is a $C_f$ such that
    $$ |\gamma(x, \smooth{\gamma} \eta(x)) \theta \int 
    (r(y, \smooth{r} \eta(y)) f(y) - r(x, \smooth{r} \eta(x)) f(x))
    q_\theta(x, dy)| \le C_f $$
    for all $x \in \IR^d$ and $\eta \in \measures$.
    Furthermore, $C_f$ only depends on the norm of $f$ and it's first two derivatives,
    i.e., 
    \[
        C_f = C(\sup_x \max_{ij} \max(f(x), \partial_{x_i} f(x), \partial_{x_i} \partial_{x_j} f(x))) .
    \] \label{gamma_B_condition}
\end{enumerate}
To keep expressions manageable, we shall also assume that 
\[
\mu_\theta(x) = r(x, \smooth{r} X(x) / N) \gamma(x, \smooth{\gamma} X(x) / N)
        - \frac{1}{\theta} F(x, \smooth{F} X(x) / N),
\]
that is, this expression is non-negative so that there is no need to take the maximum
	with zero in~(\ref{eqn:mu_defn}). (This is anyway true for 
	sufficiently large $\theta$.)
\end{assumptions}

@@

If $r(x,m)$ is independent of $m$, then the conditions are easy to 
satisfy; they just require some regularity of $r$ as a function of $x$. 
Condition~\ref{control through r} of Lemma~\ref{lem:conditions on r} is also satisfied if for example
$\|\nabla\rho_r\|\leq C\rho_r$ 
and $m\partial_mr(x,m)$, $m^2\partial_{mm}r(x,m)$ are bounded.
This is the case, for instance, if $\rho_r$ decays exponentially.
On the other hand, it might seem more natural to take $\rho_r$ to be a Gaussian 
density with parameter $\sigma_r$, say. Then, 
as we check in Lemma~\ref{lem:gamma_bound},
Condition~\ref{control through gamma} of Lemma~\ref{lem:conditions on r}
is satisfied if $\rho_\gamma$ is also
Gaussian with parameter $\sigma_\gamma$ and $\sigma_\gamma>\sigma_r$. For large enough
$\theta$, this condition guarantees that 
$\sigma_r+1/\theta <\sigma_\gamma$, so that the establishment probability of a juvenile
is controlled by individuals that are already `felt' by the fecundity kernel $\rho_\gamma$
at the location of their parent.

@@

 Writing
    $K_3 = \sup_{x,m} \max_i |\partial_{x_i} f(x)r(x, m)|$
    and 
    $K_4 = \sup_{x,m} \max_{i,j} |\partial_{x_i x_j} f(x)r(x, m)|$, since
\[\big|\partial_{x_i}\big(f(x)r(x,\rho_r*\eta(y))\big|\leq K_3\]
and
\[\big|\partial_{x_ix_j}\big(f(x)r(x,\rho_r*\eta(y))\big|\leq K_4,\]
the first term
is bounded exactly as above. For the second, 
    \begin{multline*}
        r(x, \smooth{r}\eta(y)) - r(x, \smooth{r}\eta(x))
        \\
=
        (\smooth{r}\eta(y) - \smooth{r}\eta(x)) r'(x,\smooth{r}\eta(x))
        + \frac{1}{2} (\smooth{r}\eta(y) - \smooth{r}\eta(x))^2 r''(x, \overline{m}),
    \end{multline*}
    where $\overline{m}= \kappa'\smooth{r}\eta(x) +(1-\kappa') 
\smooth{r}\eta(y)$ for some $0\leq \kappa'\leq 1$, and
    we have used $r'$ and $r''$ to denote the first and second derivatives of $r(x,m)$
with respect to the second argument.
    So, writing $K_5=\|f\|_\infty\|r'\|_\infty$ and $K_6=\|f\|_\infty\|r''\|_\infty$,
    the second term in~\eqref{eqn:q_bound_split} is bounded by
    \begin{align*}
       K_5
        \left|
            \theta \int_{\IR^d}
                (\smooth{r}\eta(y) - \smooth{r}\eta(x))
            q_\theta(x, dy)
        \right|
        +
       K_6
        \left|
            \theta \int_{\IR^d}
                (\smooth{r}\eta(y) - \smooth{r}\eta(x))^2
            q_\theta(x, dy)
        \right| .
    \end{align*}
Under Condition~\ref{control through gamma} of 
Assumptions~\ref{def:model_setup}, the right hand side is bounded by 
a constant times $\smooth{\gamma}\eta(x)+(\smooth{\gamma}\eta(x))^2$ and 
$m^2\gamma(m)$ is bounded, so therefore $|\gamma B^\theta_f|$ is bounded.

Finally, note that all bounds depended only on $\|f\|_\infty$,
$\max_i \|\partial_{x_i} f\|_\infty$, or 
$\max_{ij} \|\partial_{x_i} \partial_{x_j} f\|_\infty$.
\end{proof}

@@

\begin{proof}[Sketch]
To avoid the idea being buried in notation, we sketch the proof in the 
special case of $d=1$ and $\DG=\Delta$.
For any $f\in C_b^\infty(\IR)$,
\begin{multline}
\label{special case first moment equation}
\IE[\langle f,\eta_t\rangle] 
    =\IE[\langle f,\eta_0\rangle]
    + \IE\Big[\int_0^t\Big\langle\gamma(x, \smooth{\gamma}\eta_s(x))
    \Delta \big(f(\cdot)r(\cdot,\smooth{r}\eta_s(\cdot))\big)(x)
    \\ \qquad 
    +F(x,\smooth{F}\eta_s(x)) f(x),
    \eta_s(dx)\Big\rangle ds\Big].
\end{multline} 
We take a sequence of test functions $f_n$ increasing to the constant function 1,
and having uniformly bounded first and second derivatives
so that there is a (single) $C_1$
from Condition~\ref{gamma_B_condition} of Assumptions~\ref{def:model_setup}
such that $\gamma(x,\eta) B_{f_n}^\theta(x,\eta) \le C$ for all $x$, $\eta$, and $f_n$.
This implies that $\gamma(x,\eta) \Delta(f_n(\cdot) r(\cdot,\eta))(x) \le C_1$
for all $n$, and so in the limit, since $F$ is also bounded above,
there is a $C$ such that
\begin{align*}
    \IE[\langle 1, \eta_t\rangle]
    &=
    \IE[\langle 1, \eta_0\rangle]
    +
    \IE\Big[\int_0^t \Big\langle \gamma(x,\eta_s) \Delta r(x,\eta_s) + F(x,\eta_s) ,
    \eta_s(dx)\Big\rangle ds\Big] .
    \\ &\le
    \IE[\langle 1, \eta_0\rangle]
    +
    C \IE\Big[\int_0^t \Big\langle 1, \eta_s(dx)\Big\rangle ds\Big] .
\end{align*}
Gronwall's inequality then implies that 
$\IE[\langle 1, \eta_t(dx)\rangle]$ 
is uniformly bounded for $t\in [0,T]$, and an application of Markov's inequality
tells us that for any $\delta >0$,
$\IP[\eta_t([R,\infty])>\delta]\to 0$ as $R\to\infty$.
\end{proof}

@@

    We require that $\{(F(\lp^N_t))_{t \ge 0}\}_N$
    is tight as a sequence of real-valued c\`adl\`ag processes, for all $F$ in a subset
    of $\bar C(\lpmeasures)$, the bounded, continuous functions on $\lpmeasures$,
    that is dense with respect to uniform convergence on compact subsets.
    Lemma~\ref{lem:test_fn_tightness} shows that $\{\langle f, \lp^N_t \rangle\}_N$ is a tight sequence
    for any $f: \overline{\IR^d} \times [0,\infty) \to \IR$ with compact support
    in the level direction.
    The functions $\lp \mapsto \langle f, \lp \rangle$
    do not form not a dense subset of $\bar C(\lpmeasures)$,
    but they do separate points and vanish nowhere, so
    by the Stone-Weierstrass theorem, the algebra they generate is dense
    % in $C_0(\lpmeasures)$, the continuous functions that vanish at infinity
    % (i.e., are less than $\epsilon$ outside of a compact set, for any $\epsilon$).
    % Since $C_0(\lpmeasures)$ is dense
    in $\bar C(\lpmeasures)$ (with respect to uniform convergence on compact subsets).
    So, it suffices to show that tightness for the processes $\langle f, \lp^N_t\rangle$
    extends to finite sums and products of these processes,
    which is shown in Lemma~\ref{lem:product_tightness}.
    The fact that martingale properties are preserved under passage to the limit
    is straightforward, and can be proved in a way analgous to Lemma~\ref{lem:limit_mgale};
    we omit the proof.
    Finally, we must show that the limiting lookdown process $\lp$
    projects to the limiting process $\eta$, i.e., a solution of the martingale
    problem in Theorem~\ref{thm:nonlocal_convergence}.
    Let $N_k \to \infty$ be a sequence along which $\lp^{N_k}$ converges.
    By Theorem~\ref{thm:nonlocal_convergence},
    there is a subsequence $N_{k(j)}$ along which the projected population processes
    $\eta^{N_{k(j)}}$ converge, and the limit solves the martingale problem.
    Thus any limit point of $\lp^N$ projects to a population process $\eta$
    solving the martingale problem of Theorem~\ref{thm:nonlocal_convergence}.
\end{proof}

@@

In this section we verify one of the conditions of the Markov Mapping Theorem,
namely, that ``integrating out levels'' in the generator of the lookdown process
we obtain the generator of the projected process.
We will work with test functions of the form
$$  f(\lp) = \prod_{(x, u) \in \lp} g(x, u) = \exp\left(\langle \log g, \lp \rangle \right) . $$
Furthermore, recall that $\kappa^N(\lp)(\cdot) = \lp(\cdot \times [0, N)) / N$
is the ``spatial projection operator'',
and define the probability kernel $\Gamma^N : \measures \to \mathcal{M}(\IR^d \times [0,N))$
so that for $\eta \in \measures$, if $\hat g(x) = \int_0^N g(x, u) du / N$, then
\begin{align*}
    F^N_g(\eta)
    &:=
    \int f(\lp) \Gamma^N(\eta, d\lp) \\
    &=
    \exp\left(
        N \left\langle
            \log \frac{1}{N} \int_0^N g(x, u) du, \eta(dx)
        \right\rangle
    \right) \\
    &=
    \exp\left(
        N \left\langle \log \hat g(x), \eta(dx) \right\rangle
    \right) ,
\end{align*}
i.e., $\Gamma^N$ assigns independent labels on $[0, N]$ to each of the points in $\eta$.
It follows from Lemma~\ref{def: MP definition of limit} that for test functions of this form
the generator of $\eta^N_t$ is
\begin{align} \label{eqn:pgen_defn_again}
    \begin{split}
    \Pgen^N F^N_g(\eta)
    =
    F^N_g(\eta)
        N \theta & \bigg\langle
        \gamma(x, \eta) \int r(z, \eta) \left( \hat g(z) - 1 \right) q_\theta(x, dz)
    \\ &\qquad \qquad {}
        +
        \mu_\theta(x, \eta) \left( \frac{1}{\hat g(x)} - 1 \right)
        ,
        \eta(dx)
    \bigg\rangle .
    \end{split}
\end{align}
(Note that $f$ here differs from the $f$ used in Lemma~\ref{def: MP definition of limit}
so as to agree with standard usage in the literature on lookdown processes.)
The generator of $\lp^N_t$ is $A^N$, defined in equation~\eqref{eqn:lookdown_generator}.

@@

For the limiting process,
we now require test functions such that $g(x,u) = 1$ for all $u$ larger than some $u_0$;
As before, recall that $\kappa(\lp)(\cdot) = \lim_{u \to \infty} \lp(\cdot \times [0, u)) / u$
is the ``spatial projection operator'',
and define the probability kernel $\Gamma : \measures \to \flpmeasures$
so that for $\eta \in \measures$,
defining $h(x) = \int_0^\infty (g(x, u) - 1) du$,
\begin{align*}
    F_g(\eta)
    &:=
    \int f(\lp) \Gamma(\eta, d\lp) \\
    &=
    \exp\left(
        \big \langle
            \int_0^\infty (g(x, u) - 1) du,
            \eta(dx)
        \big \rangle
    \right) \\
    &=
    e^{ \langle h(x), \eta(dx) \rangle } .
\end{align*}
i.e., $\Gamma(\eta, \cdot)$ is the distribution of a conditionally Poisson process
with intensity a product of $\eta$ and Lebesgue measure.
It again follows from Lemma~\ref{def: MP definition of limit} that for test functions of this form
the generator of $\eta_t$ is
\begin{align} \label{eqn:pgen_infty}
    \Pgen^\infty F_g(\eta)
    &=
    F_g(\eta)
    \left\langle
        \gamma(x, \eta)
        \DG( h(\cdot) r(\cdot) )(x)
        + F(x, \eta) h(x)
        + \alpha \gamma(x, \eta) r(x, \eta) h^2(x)
        ,
        \eta(dx)
    \right\rangle .
\end{align}
The generator of $\lp_t$ is $A$, defined in equation~\eqref{eqn:limiting_lookdown_generator}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Technical Lemmas}
